### 2016-01-14 doc/tutorial/introduction.Rmd
small up

**Warning:** The findSVMSoftware functionality is made for convenience, not for performance. As all given directories has to be searched, this can slow down all I/O operations. Prevent running this function on a high performance cluster often, as might very well slowdown the whole cluster!

>>>>

**Warning:** The findSVMSoftware functionality is made for convenience, not for performance. As all given (sub)directories have to be searched, this can slow down all I/O operations. Restrain from running this function on a high performance cluster, as it might very well slowdown the whole cluster!
